\section{Modifiers and closure objects}

\begin{frame}[t,fragile]{Mutability in lambdas}
  \begin{itemize}
    \item Lambdas generate in the object function, 
          a call operator that is a \cppkey{const} member function.
    \item When the lambda is specified to be \cppkey{mutable},
          the generated call operator is \textmark{non-const}.
  \end{itemize}
\begin{lstlisting}
int ini=0;
std::generate(v.begin(), v.end(), [=]() mutable { return ini++; });
std::generate(w.begin(), w.end(), [=]() mutable -> int { return ini++; });
\end{lstlisting}
\end{frame}

\begin{frame}[t,fragile]{Closure object}
  \begin{itemize}
    \item The \textmark{evaluation} of a \textgood{lambda expression} 
          generates a temporal object called \textgood{closure object}.
    \item A \textgood{closure object} behaves as a \textmark{function object}.
    \item The type of a \textgood{lambda expression} is the same
          than the type of the \textmark{closure object}:
      \begin{itemize}
        \item Unique type.
        \item Unnamed type.
        \item Class type that is not a union.
        \item Non aggregate.
        \item Declared in the smallest scope enclosing the lambda expression.
      \end{itemize}
  \end{itemize}
\begin{lstlisting}
auto comp = [](const record & x, const record & y) { return x.id < y.id; }
std::sort(v1.begin(), v1.end(), comp);
bool test = comp(2,4);
\end{lstlisting}
\end{frame}

\begin{frame}[t]{Closure generated members}
  \begin{itemize}
    \item It has a \textbad{deleted} \textgood{default constructor}. 
    \item It has a \textbad{deleted} \textgood{copy assignment operator}.
    \item It has an \textmark{implicitly declared} \textgood{copy constructor}.
    \item May have an \textmark{implicitly declared} \textgood{move constructor}.
    \item It has an \textmark{implicitly declared} \textgood{destructor}.
    \item It has a \textgood{function call operator} 
          (\cppkey{operator()}) which is \cppkey{inline}.
      \begin{itemize}
        \item Parameters and return type are the same than those in the lambda.
        \item The operator is \cppkey{const} if the lambda was declared without \cppkey{mutable}.
      \end{itemize}
  \end{itemize}
\end{frame}

\begin{frame}[t,fragile]{Conversion to function pointer}
  \begin{itemize}
    \item \textenum{Condition}:
      \begin{itemize}
        \item It must have an \textmark{empty capture}.
      \end{itemize}
    \item Generated \textgood{conversion operator}:
      \begin{itemize}
        \item Conversion to \textgood{function pointer}.
        \item \textgood{Conversion operator} \textmark{public}, \textmark{non-virtual}, 
              \textmark{non-explicit}, and \textmark{constant}.
        \item \textmark{Same} \textgood{parameters} and \textgood{return type}.
        \item Returns a \textgood{function pointer} whose invocation has the
              \textmark{same effect} than invoking the
              \textgood{function call operator} from the \textgood{closure object}.
      \end{itemize}
  \end{itemize}
\begin{lstlisting}
void set_func(void (*f)());
set_func([]{ std::cerr << "Bye"; });
\end{lstlisting}
\end{frame}

\begin{frame}[t,fragile]{Dangers of capture by reference}
  \begin{itemize}
    \item Reference capture might give \textgood{benefits}, but \ldots
    \pause
    \item Has \textbad{dangers} when \textgood{lambda} 
          \textmark{outlives} a captured value.
      \begin{itemize}
        \item \textmark{Example}: \textgood{Callbacks}
      \end{itemize}
  \end{itemize}
\begin{lstlisting}
void f() {
  int result = 0;
  register_adder([&result](int x) { result+=x; });
  // ...
}
\end{lstlisting}
\end{frame}


