\section{Binding function arguments}

\begin{frame}[t]{Why \texttt{bind}?}
  \begin{itemize}
    \item \cppid{bind} is a new function replacing
          \cppid{bind1st} and \cppid{bind2nd}.

    \mode<presentation>{\vfill\pause}
    \item Solves problems from C++98.
      \begin{itemize}
        \item Only could bind first or (exclusive or!) second argument.
        \item Only could bind one argument.
        \item Could not be used to bind reference arguments.
        \item Need for extra function objects:
          \begin{itemize}
            \item \cppid{ptr\_fun}, \cppid{mem\_fun} y \cppid{mem\_fun\_ref}.
          \end{itemize}
      \end{itemize}

    \mode<presentation>{\vfill\pause}
    \item Header \cppid{<functional>}.
  \end{itemize}
\end{frame}

\begin{frame}[t,fragile]{Binding in function calls}
  \begin{itemize}
    \item \cppid{bind()} generates a function object from
      \begin{itemize}
        \item A callable entity (function object, function, lambda, \ldots).

\begin{lstlisting}
void f(int x, int y, int z);
auto g = std::bind(f,1,3,5);
g(); // f(1,3,5);
\end{lstlisting}

        \pause
        \item An specification of arguments binding:
          \begin{itemize}
            \item A concrete value to be used for an argument.
            \item An specification to bind a function call argument with
                  the function object parameter.
          \end{itemize}
\begin{lstlisting}
using namespace std::placeholders;
auto h = std::bind(f, 7, _1, _2);
h(3,4); // f(7,3,4);
h(1,9); // f(7,1,9);
\end{lstlisting}

        \pause
        \item All placeholders in (\cppid{\_1}, \cppid{\_2}, ...) namespace
              \cppid{std::placeholders}.
      \end{itemize}
  \end{itemize}
\end{frame}

\begin{frame}[t,fragile]{Overloaded functions}
\begin{itemize}
  \item Binding an overloaded function, requires
        non ambiguously specifying which overload to select.
\begin{lstlisting}
void f(int, int);
void f(double, double);

using namespace std::placeholders;
auto g = std::bind(f, 1, _1); // Error. f() is overloaded
auto g2 = std::bind(static_cast<void (*)(int, int)>(f), 1, _1); // OK

using task = void(*)(int,int);
auto h = std::bind(static_cast<task>(f), 1, _1); // OK
\end{lstlisting}
\end{itemize}
\end{frame}

\begin{frame}[t,fragile]{Try to bind reference parameters}
\begin{itemize}
  \item \textbad{Problem}: \cppid{bind} takes expressions as arguments.
    \begin{itemize}
      \item If the bound function takes a reference parameter,
            an \textbad{undesired effect} happens.
    \end{itemize}
\begin{lstlisting}
void f(int & i) {
  i = 42;
}

void g() {
  int x=0;
  f(x); // x is 42

  int y=0;
  using namespace std::placeholders;
  auto h = std::bind(f, _1);
  auto k = std::bind(f, y);
  h(y); // OK. Modifies y to 42
  k(); // Bad. y is 0, as bind makes a copy of y
}
\end{lstlisting}
\end{itemize}
\end{frame}

\begin{frame}[t,fragile]{Solving reference parameters binding}
\begin{itemize}
  \item The standard library offers type \cppid{reference\_wrapper<T>} 
        and two adapter functions:
    \begin{itemize}
      \item \cppid{ref(x)} for reference parameters.
      \item \cppid{cref(x)} for constant reference parameters.
    \end{itemize}

  \mode<presentation>{\vfill\pause}
  \item \textgood{Solution}: Use a reference adapter.
\begin{lstlisting}
void f(int & i) {
  i = 42;
}

void g() {
  int y=0;
  using namespace std::placeholders;
  auto k = std::bind(f, std::ref(y));
  k();
}
\end{lstlisting}
\end{itemize}
\end{frame}

\begin{frame}[t,fragile]{Member functions binding}
\begin{itemize}
  \item \cppid{bind} supports binding for non static member functions.
\begin{lstlisting}
class window {
public:
  // ...
  void click(int x, int y, status e);
  // ...
};

void f(window & v) {
  set_click_cb(std::bind(&window::click, v, _1, _2, status::normal));
  // ...
}
\end{lstlisting}
  \item Also accepts (instead of an object), a pointer, or a smart pointer.
\end{itemize}
\end{frame}

\begin{frame}[t,fragile]{Alternatives to \texttt{std::bind()}}
\begin{columns}[T]

\column{.5\textwidth}
\begin{block}{std::bind}
\begin{lstlisting}
void f(int & i) {
  i = 42;
}

void g() {
  int y=0;
  using namespace std::placeholders;
  auto h = std::bind(f, _1);
  h(std::ref(y));
}
\end{lstlisting}
\end{block}

\column{.5\textwidth}
\begin{block}{Lambdas}
\begin{lstlisting}
void f(int & i) {
  i = 42;
}

void g() {
  int y=0;
  auto h = [](int & x) { f(x); };
  h(y);
}
\end{lstlisting}
\end{block}

\end{columns}

\end{frame}
